Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-08-13 grove-paper.tex
Rough draft of "Add" section and TikZ figures for "Add" and "Change"

@@

@@

\subsubsection{Add}
TODO: explain add to the right

TODO: continuity of examples

@@

@@

@@

>>>>

TODO: Screenshot

@@

\begin{figure}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[tree layout] {
 root[as={\textbullet}] -> {
  +[as={$\texttt{+}_1$}] -> [edge label={left}] {
   22[as={$\texttt{num(22)}_2$}],
   {}
  }
 }
};
\end{tikzpicture}
\caption{A simple tree with a hole (Alternate figure)}
\label{fig:A simple tree with a hole (Alternate figure)}
\end{figure}

@@

Now that we have discussed adding holes

TODO: num(22) -> var(x)

\subsubsection{Add}

\tikzset{graphs/graph style/.style={
 tree layout,
 level sep=1cm,
 nodes={draw, rounded corners=1mm},
 edges={draw, sloped, font={\small}}
}}
\tikzset{graphs/root style/.style={
 draw=none,
 as={\textbullet}
}}
%\tikzset{graphs/every edge/.style={}
\begin{figure}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  +[as={$\texttt{+}_1$}] -> {
   x [> edge label={left}, > edge label'={2}, as={$\texttt{var(x)}_2$}],
   y [> edge label={right}, > edge label'={3}, as={$\texttt{var(y)}_3$}]
  }
 }
};
\end{tikzpicture}
\caption{Addition}
\label{fig:Addition}
\end{figure}

When users insert code into a hole, our graph model simply adds a corresponding a vertex and edge.
For example, suppose the user adds \texttt{y} as the right child of vertex~1 in Figure~\ref{fig:A simple tree with a hole (Alternate figure)}.
This corresponds to creating a vertex for the variable reference \texttt{y} and adding an edge
to that vertex from vertex~1.
Figure~\ref{fig:Addition} shows the result, where the new vertex has identifier~3.

Note that adding an edge implicitly creates.

@@

In order to change an existing vertex, we delete the existing edge to that vertex and add the new value.
For example, in

Note that while we
Note that the vertex continues to exist (this is essential for further manipulation)
Once created a vertex is never deleted.

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  +[as={$\texttt{+}_1$}] -> {
   x [> edge label={left}, as={$\texttt{var(x)}_2$}],
  }
 }
};
\path (1cm,0cm) graph[graph style] {
 y [as={$\texttt{var(y)}_3$}]
};
\end{tikzpicture}
\caption{TODO}
\label{fig:Change-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.3\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  +[as={$\texttt{+}_1$}] -> {
   x [> edge label={left}, as={$\texttt{var(x)}_2$}],
   z [> edge label={right}, as={$\texttt{var(z)}_4$}]
  }
 }
};
\path (1cm,0cm) graph[graph style] {
 y [as={$\texttt{var(y)}_3$}]
};
\end{tikzpicture}
\caption{TODO}
\label{fig:Change-b}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Change}
\label{fig:Change}
\end{figure}

@@

\subsection{Cursors}
\label{sub:Cursors}

TODO: cursors are informational
